---
layout: post
title: "Episode I: The Phantom Menace //TITLE HERE"
author: "A supreme undergrad //AUTHOR HERE"
date: "February 20, 2020 at exactly 20 seconds after 2:20 pm (woah) //date here"
---

```{r setup, echo = FALSE, message = FALSE}
library(knitr)
```

```{r pkgs, echo = FALSE, message = FALSE}
# Initialize Environment
#########################

# Set CRAN location for installing packages
############################################
r <- getOption("repos")
r["CRAN"] <- "http://cran.wustl.edu"
options(repos = r)
rm(r)

## Helper function to install a CRAN package if not installed and load
######################################################################
use_package <- function(p) {
if (!is.element(p, installed.packages()[,1]))
  install.packages(p, dep = TRUE)
library(p, character.only = TRUE)
}

# Load base R libraries (no need to install)
#############################################
library(grid)

# Check and install CRAN packages (may need more)!!!!!!
#######################################################
use_package('png') # For importing pngs
use_package('grImport2') # For importing svg graphics
use_package('TDA')
use_package('ggplot2') # For some nice plots based in the grid package
```

## Overview


### Questions
  
* What defines meaning? 
* Does P = NP? 
* Are we alone in the universe?

//Add your big questions here

### Objectives

By the end of this tutorial you should be able to:

* Parallel park a train
* End world hunger
* Develop your very own R package 'TDA'

<!--- the syntax '---' creates a line seperator, a nice way to split up concepts -->

---

## Content
Blibbity blah blah, here is my sweet content, add yours here.

### Subsections
Blibbity blah blah, this is a subsection, make as many or as few as you'd like using increasing numbers of # symbols.

### Subsection with code chunk
Here's how to add a code chunk:

```{r plot_two_Circles, message=FALSE, echo=TRUE}
library('TDA')
library('spatstat')

x <- circleUnif(50,10)
plot(x, pch = 18, xlab = "", ylab = "")

```

Or if we just want plots and not the code that generated them:

```{r plot_two_Circles_Again, message=FALSE, echo=FALSE}
library('TDA')
library('spatstat')
x <- circleUnif(100,1.5)
Nice_Cycle <- as.ppp.data.frame(x,c(-2,2,-2,2))
plot(Nice_Cycle, pch = 18, xlab = "", ylab = "")

xppp <- as.ppp.data.frame(Nice_Cycle,c(-2,2,-2,2))
Angsty_Cycle <-rjitter(xppp,0.25)
plot(Angsty_Cycle, pch = 16, xlab = "", ylab = "")
```

---
## Another Section With a Challenge

Yada yada yada, clustering, manifolds

### Challenge
1. Create your own cycle with 10 points and radius = 10.
2. Make sure that the axes are not labeled with a range of numbers.

### Solution
```{r plot_one_Circle, message=FALSE, echo=TRUE}

x <- circleUnif(10, 10)
Nice_Cycle <- as.ppp.data.frame(x,c(-10,10,-10,10))
plot(Nice_Cycle, pch = 18, xlab = "", ylab = "")
```
